Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-03 manuscript.tex
Finished reviewing paper

\abstract
% Context, Aims, Methods, Results, Conclu (not mandatory)
{Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
Stellar activity can be probed by measuring time dependent variations in the shape of the cross-correlation function (CCF), often estimated using the different moments of the modeled CCF. Therefore estimating the moments of the CCF with high precision is essential to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}
%
{We propose to estimate the moments of the CCF by fitting a model using a Skew Normal (SN) density shape, which unlike the commonly employed Normal density, includes an skewness parameter to capture the asymmetry of the CCF induced by stellar activity, but also the natural asymmetry induced by convective blueshift.}
%
{The performance of the proposed method is compared to the Normal density using both simulated and real observations with varying levels of activity and signal-to-noise ratio (SNR) levels.}
%We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels. In each case, we compare the results obtained by fitting to the CCF respectively a Normal and a SN.  We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.
%
{When considering the real observations, the correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are stronger when using the parameters derived from the SN than the Normal approach. 
This suggests that the CCF asymmetry and the CCF width derived using a SN may be more sensitive to stellar activity, which can be helpful with estimating stellar rotational periods and generally characterizing the stellar activity signals.
The estimated uncertainties in the estimated RVs using the proposed SN approach are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal, and the estimated uncertainties on the SN asymmetry parameter are on average $15\%$ smaller than the commonly used Bisector Inverse Slope Span (BIS SPAN) approach for estimating the asymmetry of the CCF. }
{XXX \jessi{It looks like we still need to add conclusions here}}
%
%{The derived benefits of using the proposed SN approach includes an asymmetry parameter along with several options for estimating the RV, while the Normal model only includes an RV estimate and requires a separate procedure for estimating the asymmetry.  Furthermore, the estimated uncertainties on the RVs and the asymmetry parameter are smaller in the SN setting.}
%The correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations. Therefore the CCF asymmetry and the CCF width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals. The precision on the estimated set of RVs, derived using the median of the fitted SN densities are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal. In addition, the uncertainties related to the asymmetry parameter derived from the SN are on average $15\%$ smaller than the ones calculated on the common Bisector Inverse Slope Span (BIS SPAN). We strongly encourage the use of the SN density rather than the Normal density, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RVs and the the asymmetry parameter are smaller than the one estimated with the Normal fit.

@@

%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 3.6in]{HD12862_gamma_vs_bisspan.pdf} 
\includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
   \caption{\emph{Left: }Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B. As we can see with the strong correlation, those two parameters measure the CCF asymmetry in the same way. \emph{Top right:} RVs as function of Julian Day for Alpha Centauri B in 2010. The RVs are retrieved using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan crosses) of a SN density fitted to the CCF. \emph{Bottom right:} RV differences between the RVs derived when using the SN density and the RV derived when using the Normal density.}
   \label{fig:alphacent:corr.gamma}
\end{center}
\end{figure*}
%

@@

\xavier{In this section, we investigate how the noise of the CCF influence the CCF parameters derived either by a Normal density or a SN density fit. Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other. Therefore, we cannot simply vary each point in the CCF with their respective error bar and then recalculate the best SN or Normal density fit, to see how the CCF noise influences N mean RV, SN mean RV, SN median RV, FWHM, SN FWHM, BIS SPAN and $\gamma$. We therefore started from the spectrum, for which we know that each point is totally independent of the others. The standard error on each point of the spectrum is given by the photon noise, which follows a Poisson law and is therefore obtained by taking the square root of the measured flux.}

\xavier{We applied the following method to estimate the error bars on the different parameters derived from the CCF. We first modify the values of all the points in the spectrum given their respective error bars. To do so we added to each point the value randomly drawn from a Gaussian distribution centered on the value of the point and with standard deviation the square root of the flux. We then calculated the CCF from this spectrum using the method presented in \citet{Pepe-2002a}, fitted either a Normal or SN density to this CCF and recorded the different parameters. We redo this process a hundred times, which gives us at the end, a distribution for each CFF parameter. The standard deviations of the obtained distributions is then associated to the noise of each CCF parameters.}

\xavier{We measured the standard deviation of each CCF parameters for all the CCF of HD215152, HD192310 and Corot-7. This gives us an information of how the noise on each CCF parameter varies as a function of SNR. In this case, the SNR, measured at 550 nm on the original spectra, varies between 10 and 500. The results can be seen in Fig.~\ref{fig:se}. In the top plots of this figure, we show the standard errors for the different RV, width and asymmetry estimates. Note that because BIS SPAN and $\gamma$ does not have the same units, we used the slope of the correlation between those two parameters to transform $\gamma$ in \ms (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star). In the bottom plots, we show the ratio between the standard errors measured when using the SN parameters and the Normal parameters. Values smaller or larger than one will imply that standard errors fro the SN parameters are more or less precise, respectively.}

\xavier{Looking at the estimates for the RV, we see that they all follow a similar exponential decay. Although we plot the data for three different stars, we do not see any offsets in this decay, which implies that the SNR at 550 nm is the main contributor to the precision measured in RV. This is not surprising as the 3 stars studies are all main sequence K-dwarfs. When comparing the three different estimates for the RV, we see that SN mean RV presents standard errors that are 60\% larger than what N mean RV gives. On the opposite, SN median RV gives errors 10\% more precise than N mean RV. Regarding the parameters describing the width of the CCF, FWHM and SN FWHM have the same standard errors. Finally, for the asymmetry parameters, we see that $\gamma$, derived from the SN, is 15\% more precise than BIS SPAN. In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV, we are able to improve by 10\% the precision on the RV, 15\% the precision on the asymmetry, and this without degrading the precision on the width estimate. SN mean RV should not be use to derive RVs, except perhaps for stars for which the photon noise is not the dominant source of noise, as the precision on this parameter if 60\% worse than the precision on the RV derived from a Normal density fit.}
%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter. When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles). However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN. Note that for the asymmetry, the error in BIS SPAN is in \kms. To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
   \label{fig:se}
\end{center}
\end{figure*}

@@

\xavier{When fitting a SN density to the CCF, it is possible at once to retrieve parameters that describe the RV, i.e. the CCF barycenter, the amplitude, also called the contrast, the width, and the asymmetry of the CCF. For the RV, we investigated the use of the mean and the median of the SN density. Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry, by using $\gamma$, the skewness parameter of the SN density.

When we tested the SN density fit to the CCF provided by the SOAP 2.0 code, that simulate the activity signal induced by a spot or a faculae on a solar-like star, we arrived to the conclusion that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual method. By more sensitive, we mean here that the correlation between the skewness and either the mean or median of the SN density is stronger than between BIS SPAN and the mean of a Normal density. Moreover, the correlation between the FWHM and the CCF barycenter is also stronger when using the parameters from the SN compared to the parameters from the Normal. We also confirmed the behavior that the SN parameters are more correlated than the Normal parameters in the case where a planetary signal is added the to stellar activity modeled by SOAP 2.0.

We also present in this paper a new function to correct for stellar activity signals. Generally, when fitting for planetary signals, people use a model composed of one or several Keplerians to account for the planets, in addition to a linear combination with the FWHM and BIS SPAN of the CCF to account for stellar activity signals. The new function propose to add a linear dependency with the amplitude of the CCF retrieved either by the SN or Normal density fit, and a interaction term between the asymmetry and the width parameters. On the simulated data from SOAP 2.0, this new model allows to mitigate stellar activity signals by a factor of 2 and 3.5 compared to the model generally used, for the faculae and spot, respectively.

When moving to real data, we arrived to the same conclusions regarding the strength of the correlation between the asymmetry and the CCF barycenter, as well as between the width and the CCF barycenter. We note however that although in the case of the simulated data, the stronger asymmetry-RV correlation was found between $\gamma$ and the median of the SN, in the case of real data, it was between $\gamma$ and the mean of the SN. This can be due to the fact that in SOAP 2.0, the faculae is not modelled properly, as it uses as emerging spectrum the one from a spot. We know that the temperature between a spot and a faculae is significantly different, therefore their spectra should be different. In addition, there is always several active regions on a star, at different locations in longitude and latitude. This could also be responsible for the fact that we do not observe the same behavior for the mean and the median of the SN when we compare the SOAP 2.0 simulation and real data. Nevertheless, in both the simulated case and the real cases, the parameters derived from the SN are more sensitive to activity than the parameters derived from a Normal fit. In addition, the correlation between the asymmetry and the mean of the SN is always stronger than any other parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.

@@

Having an estimate of the RV that is more sensitive to stellar activity, like the mean of the SN, can help us to probe better stellar rotational periods, or understand better the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}. We saw in the preceding section that the RV estimated by the mean of the SN is 60\% noisier than the RV derived by the mean of the Normal. This is not necessarily a negative aspect. Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized by increasing its induced RV amplitude even if the white noise is 60\% larger.

Even if the different RV estimates have different amplitudes, once we apply our new correction for stellar activity, we arrive exactly to the same RV rms in the residuals, meaning that for activity correction, the SN parameters does not help. We note that when comparing the activity correction presented in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, we only see a slight improvement brought by our proposed correction.

We checked if some RV estimates were better at finding planets in RV data affected by observed stellar signals. When using the new correction proposed in this paper to mitigate the effect from stellar activity, and when assesing planetary detection based on periodogram analysis, we find very similar detection limits for the three RV estimates presented in this paper. Therefore it seems that any of the RV estimate can be used to search for planetary signals.

Finally, we investigated the precision of each of the SN and Normal parameters including the BIS SPAN. It turns out that the mean of the SN should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than when taking the mean of the Normal distribution. However, the median of the SN should be used, as it is 10\% more precise than the mean of the Normal. Regarding the asymmetry estimates, we observe that $\gamma$ has a precision15\% better than the BIS SPAN. It is therefore clear in this case that the SN parameters are more precise to measure the barycenter and the asymmetry of the CCF.}

@@

\xavier{When searching for small-mass exoplanets using the RV technique, it is crucial to get the best precision possible on the determination of the RV, but also to measure precisely the shape variations of the CCF, as such variations are induced by stellar activity, and not by planets. The correlations between the width of the CCF and the RV, and the asymmetry of the CCF and the RV are used as a way to assess if the measurements are affect by stellar activity signals, therefore, the stronger the correlation, the better we can probe small level of stellar activity.

In this paper we introduced a novel approach based on the Skew Normal (SN) density to retrieve the RV and shape variation of the CCF. This new method is compared to the usual one, where a Normal density is fitted to the CCF to retrieve the information on the RV and the width of the CCF, and a bisector analysis allows to retrieve the asymmetry of the CCF using the BIS SPAN. In addition, we also compare this novel approach to other parameterisations of the CCF asymmetry that have been shown to be more sensitive to activity signals \citep[][]{Boisse-2011,Figueira-2013}.

@@

Because of these advantages of using the SN parameters compared to the Normal parameters, BIS SPAN, and all the asymmetry parameters described in \citet{Boisse-2011} and \citet{Figueira-2013}. we strongly encourage the community of using this new parametrization of the CCF.
Correlations between the asymmetry and the mean of the SN, and between the width and the mean of the SN should be used to probe better stellar signals in RV data, and the median of the SN should be used as the new definition for RV.
}

@@

In this Appendix we present the analyses conducted on other 4 stars: HD192310, HD10700, HD215152 and finally Corot-7.

\umberto{Add further information about the stars here presented.}\xavier{}

Table \ref{table:summaryStars} summarizes the results obtained by the SN fit and the some of the results based on the Normal fit. The results are all consistent with the conclusions derived by the analyses on Alpha Centauri B. The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and RV for all the considered stars. The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV for three of the four stars.  Also for all these stars we corrected the originally estimated RVs from spurious variations in RVs caused by stellar activity, using Eq. \ref{eq:RV:correction}. Fig. \ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RVs. While the Normal and SN residuals, once corrected for stellar activity, are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$, the results of the analyses on the star $\text{HD}215152$ (whose CCF's have lower SNR respect to the previous two analyzed stars) suggest that the residuals for the Normal are $0.054 \ms$ higher than the residuals retrieved with the SN analysis. Finally, the results of the analysis on $\text{Corot }7$, whose CCF's have lowest SNR, show that once corrected from stellar activity the residuals from the Normal fit are $0.336 \ms$ higher than the residuals retrieved with the SN analysis.

>>>>

\abstract
% Context, Aims, Methods, Results, Conclu (not mandatory)
{\xavier{@Umberto, Update the abstract please.} Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
Stellar activity can be probed by measuring time dependent variations in the shape of the cross-correlation function (CCF), often estimated using the different moments of the modeled CCF. Therefore estimating the moments of the CCF with high precision is essential to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}
%
{We propose to estimate the moments of the CCF by fitting a model using a Skew Normal (SN) density shape, which unlike the commonly employed Normal density, includes an skewness parameter to capture the asymmetry of the CCF induced by stellar activity, but also the natural asymmetry induced by convective blueshift.}
%
{The performance of the proposed method is compared to the Normal density using both simulated and real observations with varying levels of activity and signal-to-noise ratio (SNR) levels.}
%We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels. In each case, we compare the results obtained by fitting to the CCF respectively a Normal and a SN.  We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.
%
{When considering the real observations, the correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are stronger when using the parameters derived from the SN than the Normal approach. 
This suggests that the CCF asymmetry and the CCF width derived using a SN may be more sensitive to stellar activity, which can be helpful with estimating stellar rotational periods and generally characterizing the stellar activity signals.
The estimated uncertainties in the estimated RVs using the proposed SN approach are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal, and the estimated uncertainties on the SN asymmetry parameter are on average $15\%$ smaller than the commonly used Bisector Inverse Slope Span (BIS SPAN) approach for estimating the asymmetry of the CCF. }
{XXX \jessi{It looks like we still need to add conclusions here}}
%
%{The derived benefits of using the proposed SN approach includes an asymmetry parameter along with several options for estimating the RV, while the Normal model only includes an RV estimate and requires a separate procedure for estimating the asymmetry.  Furthermore, the estimated uncertainties on the RVs and the asymmetry parameter are smaller in the SN setting.}
%The correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations. Therefore the CCF asymmetry and the CCF width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals. The precision on the estimated set of RVs, derived using the median of the fitted SN densities are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal. In addition, the uncertainties related to the asymmetry parameter derived from the SN are on average $15\%$ smaller than the ones calculated on the common Bisector Inverse Slope Span (BIS SPAN). We strongly encourage the use of the SN density rather than the Normal density, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RVs and the the asymmetry parameter are smaller than the one estimated with the Normal fit.

@@

%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 3.6in]{HD12862_gamma_vs_bisspan.pdf} 
\includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
   \caption{\xavier{Slope should be 720, Legend for subplot bottom right should be N mean RV and bot N mean RV RV}. \emph{Left: }Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B. As we can see with the strong correlation, those two parameters measure the CCF asymmetry in the same way. \emph{Top right:} RVs as function of Julian Day for Alpha Centauri B in 2010. The RVs are retrieved using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan crosses) of a SN density fitted to the CCF. \emph{Bottom right:} RV differences between the RVs derived when using the SN density and the RV derived when using the Normal density.}
   \label{fig:alphacent:corr.gamma}
\end{center}
\end{figure*}
%

@@

In this section, we investigate how the noise of the CCF influences the CCF parameters derived either by a Normal density or a SN density fit. Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other. Therefore, we cannot simply vary each point in the CCF with their respective error bar and then recalculate the best SN or Normal density fit, to see how the CCF noise influences N mean RV, SN mean RV, SN median RV, FWHM, SN FWHM, BIS SPAN and $\gamma$. We therefore started from the spectrum, for which we know that each point is totally independent of the others. The standard error on each point of the spectrum is given by the photon noise, which follows a Poisson law and is therefore obtained by taking the square root of the measured flux.

We applied the following method to estimate the error bars on the different parameters derived from the CCF. We first modify the values of all the points in the spectrum given their respective error bars. To do so we added to each point the value randomly drawn from a Gaussian distribution centered on the value of the point and with standard deviation the square root of the flux. We then calculated the CCF from this spectrum using the method presented in \citet{Pepe-2002a}, fitted either a Normal or SN density to this CCF and recorded the different parameters. We redo this process a hundred times, which gives us at the end, a distribution for each CFF parameter. The standard deviations of the obtained distributions is then associated to the standard errors of each CCF parameters.

We measured the standard errors of each CCF parameters for all the CCFs of HD215152, HD192310 and Corot-7. This gives us an information of how the noise on each CCF parameter varies as a function of SNR. In this case, the SNR, measured at 550 nm on the original spectra, varies between 10 and 500. The results can be seen in Fig.~\ref{fig:se}. In the top plots of this figure, we show the standard errors for the different RV, width and asymmetry estimates. Note that because BIS SPAN and $\gamma$ does not have the same units, we used the slope of the correlation between those two parameters to transform $\gamma$ in \ms (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star). In the bottom plots, we show the ratio between the standard errors measured when using the SN parameters and the Normal parameters. Values smaller or larger than one will imply that standard errors from the SN parameters are more or less precise, respectively.

Looking at the estimates for the RV, we see that they all follow a similar exponential decay. Although we plot the data for three different stars, we do not see any offsets in this decay, which implies that the SNR at 550 nm is the main contributor to the precision measured in RV. This is not surprising as the three stars studied here are all main sequence K-dwarfs.

When comparing the three different estimates for the RV, we see that SN mean RV presents standard errors that are 60\% larger than what N mean RV gives. On the opposite, SN median RV gives errors 10\% more precise than N mean RV. Regarding the parameters describing the width of the CCF, FWHM and SN FWHM have the same standard errors. Finally, for the asymmetry parameters, we see that $\gamma$, derived from the SN, is 15\% more precise than BIS SPAN. In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV, we are able to improve by 10\% the precision on the RV, 15\% the precision on the asymmetry, and this without degrading the precision on the width estimate. SN mean RV should not be use to derive precise RVs, except perhaps in specific conditions described below, as the precision on this parameter is 60\% worse than the precision on the RVs derived when using the mean of a Normal density fit to the CCF.
%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameters. When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved when fitting a Normal density (red triangles). However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. The use of the asymmetry SN parameter $\gamma$ leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN. Note that for the asymmetry, the error in BIS SPAN is in \ms. To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
   \label{fig:se}
\end{center}
\end{figure*}

@@

When fitting a SN density to the CCF, it is possible at once to retrieve parameters that describe the RV, i.e. the CCF barycenter, the amplitude, sometimes called the CCF contrast, the width, and the asymmetry of the CCF. To estimate the RV, we investigated the use of the mean and the median of the SN density. Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry by using $\gamma$, the skewness parameter of the SN density.

When we tested the SN density fit to the CCFs provided by the SOAP 2.0 code, that simulate the activity signal induced by a spot or a faculae on a solar-like star, we arrived to the conclusion that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual method. By more sensitive, we mean here that the correlation between the skewness and either the mean or median of the SN density is stronger than between BIS SPAN and the mean of a Normal density. Moreover, the correlation between the FWHM and the CCF barycenter is also stronger when using the parameters from the SN compared to the parameters from the Normal. We also confirmed the behavior that the SN parameters are more correlated than the Normal parameters in the case where a planetary signal is added the to stellar activity modeled by SOAP 2.0.

We also present in this paper a new function to correct for stellar activity signals. Generally, when fitting for planetary signals, people use a model composed of one or several Keplerians to account for the planets, in addition to a linear combination with the FWHM and BIS SPAN of the CCF to account for stellar activity signals. The new function proposes to add a linear dependency with the amplitude of the CCF retrieved either by the SN or Normal density fit, and an interaction term between the asymmetry and the width parameters. On the simulated data from SOAP 2.0, this new model allows to mitigate stellar activity signals by a factor of 2 and 3.5 better compared to the model generally used, for the faculae and spot, respectively.

When moving to real data, we arrived to the same conclusions than the results of the SOAP 2.0 simulations regarding the strength of the correlation between the CCF asymmetry and the RV, as well as between the CCF width and the RV. We note however that although in the case of the simulated data, the stronger asymmetry-RV correlation was found between $\gamma$ and the median of the SN, in the case of real data, it was found between $\gamma$ and the mean of the SN. This can be due to the fact that in SOAP 2.0, the faculae is not modelled properly, as it uses as emerging spectrum the one from a spot. We know that the temperature between a spot and a faculae is significantly different, therefore their spectra should be different. In addition, there is always several active regions on a star, at different locations in longitude and latitude, which is not the case in our SOAP 2.0 simulations were only one active region was modelled at a time. This could also be responsible for the fact that we do not observe the same behavior for the mean and the median of the SN when we compare the SOAP 2.0 simulation and real data. Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are more sensitive to activity than the parameters derived from a Normal fit. In addition, the correlation between the asymmetry and the mean of the SN is always stronger than any other parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.

@@

Having an estimate of the RV that is more sensitive to stellar activity, like the mean of the SN, can help us to probe better stellar rotational periods, or understand better the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}. We saw in the preceding section that the RV estimated derived by the mean of the SN is 60\% noisier than the RV derived by the mean of the Normal. This is not necessarily a negative aspect. Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring SN mean RV, even if the white noise in the data is increased by 60\%.

Even if the different RV estimates have different amplitudes, once we apply our new correction for stellar activity, we arrive exactly to the same RV rms in the residuals, meaning that for an activity correction based on a linear combination of CCF parameters, the SN density fit does not help. We note that when comparing the activity correction presented in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, we only see a slight improvement brought by our proposed correction.

We checked if some RV estimates were better at finding planets in RV data affected by observed stellar signals. When using the new correction proposed in this paper to mitigate the effect from stellar activity, and when assesing planetary detection based on aperiodogram analysis, we find very similar detection limits for the three RV estimates presented in this paper. Therefore it seems that any of the RV estimate can be used to search for planetary signals.

Finally, we investigated the precision of each of the SN and Normal parameters including the BIS SPAN. It turns out that the mean of the SN should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than when taking the mean of the Normal distribution. However, the median of the SN should be used, as it is 10\% more precise than the mean of the Normal. Regarding the asymmetry estimates, we observe that $\gamma$ has a precision15\% better than the BIS SPAN. It is therefore clear in this case that the SN parameters are more precise to measure the RV and the asymmetry of the CCF.

@@

When searching for small-mass exoplanets using the RV technique, it is crucial to get the best precision possible on the determination of the RV, but also to measure precisely the shape variations of the CCF, as such variations are induced by stellar activity, and not by planets. The correlations between the width of the CCF and the RV, and the asymmetry of the CCF and the RV are used as a way to assess if the measurements are affect by stellar activity signals, therefore, the stronger those correlations are, the better we can probe low level of stellar activity.

In this paper, we introduced a novel approach based on the Skew Normal (SN) density to retrieve the RV and shape variation of the CCF. This new method is compared to the usual one, where a Normal density is fitted to the CCF to retrieve the information on the RV and the width of the CCF, and a bisector analysis allows to retrieve the asymmetry of the CCF using the BIS SPAN. In addition, we also compare this novel approach to other parameterisations of the CCF asymmetry that have been shown to be more sensitive to activity signals \citep[][]{Boisse-2011,Figueira-2013}.

@@

Because of these advantages of using the SN parameters compared to the Normal parameters, BIS SPAN, and all the asymmetry parameters described in \citet{Boisse-2011} and \citet{Figueira-2013}. we strongly encourage the community of using this new parametrization of the CCF.
Correlations between the asymmetry and the mean of the SN, and between the width and the mean of the SN should be used to probe better stellar activity signals in RV data, and the median of the SN should be used as the new definition for RV.

@@

In this Appendix we present the same analysis as presented in Sec.~\ref{sec:4} for those four main-sequence stars: HD192310 (K2V), HD10700 (G8V), HD215152 (K3V) and finally Corot-7 (K0V).

Table \ref{table:summaryStars} summarizes the results obtained by the SN fit and some of the results based on the Normal fit. The results are all consistent with the conclusions derived by the analyses on Alpha Centauri B. The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and RV or between the asymmetry parameters derived in \citet{Boisse-2009} and \citet{Figueira-2013} and RV for all the considered stars. The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV for three of the four stars.  Also for all these stars we corrected the originally estimated RVs from spurious variations in RVs caused by stellar activity, using Eq. \ref{eq:RV:correction}. Fig. \ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RVs. While the Normal and SN residuals, once corrected for stellar activity, are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$, the results of the analyses on $\text{HD}215152$ and Corot-7, whose measurements have lower SNR with respect to the previous two analyzed stars, suggest that the residuals for the Normal are 0.05 and 0.34\,\ms\,higher than the residuals retrieved with the SN analysis, respectively.

\small{
\begin{table*}[!t]
\caption{Subset of notable correlations between the asymmetry or the FWHM parameters and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$. The complete results of the analyses of the correlations for the four stars are presented in Fig. \ref{fig:Gliese785:corrPlot}--\ref{fig:Corot7:corrPlot}.}
\label{table:summaryStars}
\begin{center}
\begin{tabular}{ccccccccc}
\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{SN mean RV})$}\\
\hline
\hline
 $\text{HD}192310  $          &    $1577$    & $0.888$ & $786$ & $0.669 (0.64; 0.695)$\\
\hline
 $\text{HD}10700 $            &    $7928$    & $0.78$ & $604$ & $0.322 (0.302; 0.342)$\\
\hline
 $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $794$ & $0.571 (0.485; 0.646)$ \\
\hline
 $\text{Corot }7$     &     $173$    &  $0.814$  & $607$ & $0.561 (0.450; 0.656)$  \\
\hline
\rule{0pt}{2ex}    & & & &\\
\textbf{Star}          &\textbf{$\text{R}(\text{Bis-Span}, \text{N mean RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{N mean RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{N mean RV})$} \\
\hline
\hline
 $\text{HD}192310  $& $0.329 (0.285; 0.373)$  & $-0.333 (-0.376; -0.289)$ & $0.666 (0.637; 0.692)$ & $0.476 (0.4367; 0.514)$\\
\hline
 $\text{HD}10700 $ & $-0.073 (-0.095; -0.0051)$ & $0.127 (0.105; 0.148)$ & $0.421 (0.403; 0.439)$ & $0.529 (0.513; 0.545)$ \\
\hline
 $\text{HD}215152 $& $-0.067 (-0.184; 0.052)$  & $0.269 (0.155; 0.376)$ & $0.210 (0.094; 0.321)$ & $-0.138 (-0.253; -0.020)$ \\
\hline
 $\text{Corot }7$ & $0.092 (-0.058; 0.238)$ & $-0.335 (-0.228; -0.082)$ & $-0.709 (0.626;0.776)$ & $0.595 (0.489; 0.683)$ \\
\hline
\rule{0pt}{2ex}    & & & &\\
\end{tabular}
\end{center}
\end{table*}
}

%HD192310
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
   \caption{\xavier{Update correposnding to similar figures in Sec 5}. Correlation between the asymmetry parameters and the RVs for $\text{HD}192310$. The last three plots show the correlation between the FWHM and the RVs for $\text{HD}192310$ using respectively the SN and the Normal fits. The p--values associated with each $R$ is statistically different from $0$.}
   \label{fig:Gliese785:corrPlot}
\end{center}
\end{figure*}

\begin{figure*} 
\begin{center}
\includegraphics[height = 6in]{NEW_CORRECTIONHD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{\xavier{Update correposnding to similar figures in Sec 5}. Set of RVs for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq. \ref{eq:RV:correction}. Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
   \label{fig:HD192310:correctionRV}
\end{center}
\end{figure*}

%HD10700
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
   \caption{\xavier{Update correposnding to similar figures in Sec 5}. Correlation between the asymmetry parameters and the RVs for $\text{HD}10700$. The last three plots show the correlation between the FWHM and the RVs for $\text{HD}10700$ using respectively the SN and the Normal fits. The p--values associated with each $R$ is statistically different from $0$.}
   \label{fig:Tau:corrPlot}
\end{center}
\end{figure*}

\begin{figure*} 
\begin{center}
\includegraphics[height = 6in]{NEW_CORRECTIONHD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{\xavier{Update correposnding to similar figures in Sec 5}. Set of RVs for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq. \ref{eq:RV:correction}. Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
   \label{fig:HD10700:correctionRV}
\end{center}
\end{figure*}
